---
title: "Exploratory Data Analysis (EDA)"
format: html
editor: visual
---

**Exploratory Data Analysis**

As stated per the notes, Exploratory Data Analysis consists of a few steps:

-   Understanding and analyzing how the data is stored

-   Do basic data validation

-   Determine how many missing values are there for each variable (check for missing values)

-   Clean up data when necessary

-   Investigate the distributions of the data

-   Then, apply the data transformations to the original data

**Data Structure**

Through the **str()** command, we will check the structure of the data. **str()** stands for **structure.**

```{r}
#str(diabetes_health_indicators)
```

**Basic Data Validation**

In order to perform the process of **basic data validation,** we could use the **psych::describe()** for a dataset. The **"psych"** package is an R package which contains various functions used for data analysis; and contains tools for data visualization, factor analysis, reliability analysis, correlation analysis, and more.

```{r}
#psych::describe(diabetes_health_indicators)
```

**Determining the Rate of Missing Values**

```{r}
#colSums(is.na(diabetes_health_indicators))
```

Determine Rate of Missing Values

```{r}
#sum_na <- function(column){
 #sum(is.na(column))
#}
#na_counts <- diabetes_health_indicators |>
 #summarize(across(everything(), sum_na))
#na_counts
```

Clean Up Data as Needed

```{r}
#diabetes_health_indicators |>
 #drop_na(names(diabetes_health_indicators)[na_counts < 30])

```

Imputing Values

```{r}
#diabetes_health_indicators <- diabetes_health_indicators |>
 #replace_na(list(BMI = mean(diabetes_health_indicators$BMI, na.rm = TRUE),
 #Height = mean(diabetes_health_indicators$Height, na.rm = TRUE)))
#diabetes_health_indicators
```

Let's create factor versions of our three variables.

```{r}
#unique(diabetes_health_indicators$Sex)
```

Contingency Tables

```{r}
#diabetes_health_indicators |>
 #group_by(Sex) |>
 #drop_na(Sex) |>
 #summarize(count = n())
```
